Traditional agroforestry systems in Timor-Leste can store large amounts of carbon in both soil and biomass

### 2024-02-09 manuscript.Rmd
new version of the figures after discussions in feb 2024

data_soil_C <- data_soil[, .(meanSC = sum(Cstock), clay = mean(as.numeric(CLAY), na.rm = TRUE)), .(N_PLOT)]
```

@@

data_soil_unc = data_soil_unc[, .(Cstock = sum(
  (h1 - h0) * 1e8 *  
    BD * Corg/100 * (1-CF) * 1e-6  
)),
.(N_PLOT, iter)
]

data_soil_unc = data_soil_unc[, .(
  lwrSC = quantile(Cstock, 0.025), 
  uprSC = quantile(Cstock, 0.975)), 
  .(N_PLOT)]
```

```{r combine-agb-soc-data}
# combine AGB and soil C
dataC <- merge(data_agb, data_soil_C)

# add soil carbon uncertainty
dataC <- merge(dataC, data_soil_unc)

@@

```{r tab-mean, results = "show"}
# average values per village and SAF type
dataC_mean <- dataC[, .(AGC = paste0(round(mean(meanAGC), 2), " +/- ", round(sd(meanAGC)/sqrt(length(meanAGC)), 2)), 
                        SC = paste0(round(mean(meanSC), 2), " +/- ", round(sd(meanSC)/sqrt(length(meanSC)), 2))),
                        .(ID_AF)]
dataC_mean$ID_AF <- factor(dataC_mean$ID_AF, levels = c("CF", "SP", "YA", "HG", "FG"))
dataC_mean = dataC_mean[order(dataC_mean$ID_AF),]
knitr::kable(dataC_mean, col.names = c("Agroforestry system", "Aboveground carbon (Mg/ha)", "Soil organic carbon (Mg/ha)"))
write.csv(dataC_mean, file = "tables/C_mean_SAF.csv", row.names = FALSE)
```

```{r fig-1-map, fig.height =6, fig.width = 7}
# required packages
# req_packages <- c("BIOMASS", "readxl", "data.table", "ggmap", "ggplot2")

@@

data_plot[, village := substr(ID_VILLAGE, 1, 1)]
data_plot[village == "S", village := "Samalari"]
data_plot[village == "G", village := "Gariuai"]

data_box = data_plot[, .(xc = mean(long), yc = mean(lat)), .(village)]
data_box[village == "Gariuai", `:=`(w = 0.1, xc = xc + 0.001)]
data_box[village == "Samalari", w := 0.05]
data_box[, `:=`(x1 = xc - w/2, x2 = xc + w/2, y1 = yc - w/2, y2 = yc + w/2)]

@@

# geodata::elevation_3s(lon= c(data_box[village == "Samalari"]$x1), 
#                       lat= c(data_box[village == "Samalari"]$y1), 
#                       path = "data")
timor_map <- map_data("world", region = "Timor-Leste")

# get elevation information
elev = as.data.frame(terra::rast("data/srtm_62_14.tif"), xy = TRUE)
elevS <- subset(elev, x > data_box[village == "Samalari"]$x1 & 
                  x < data_box[village == "Samalari"]$x2 & 
                  y > data_box[village == "Samalari"]$y1 & 
                  y < data_box[village == "Samalari"]$y2)
elevG <- subset(elev, x > data_box[village == "Gariuai"]$x1 & 
                  x < data_box[village == "Gariuai"]$x2 & 
                  y > data_box[village == "Gariuai"]$y1 & 
                  y < data_box[village == "Gariuai"]$y2)

# Timor map (fig 1a)
g1 = ggplot(timor_map) + 
  # lims(x = c(124.5, 127.5), y = c(-9.2, -8.3)) +
  #ggmap::ggmap(basemap) +
  geom_polygon(aes(x = long, y = lat, group = group), fill="lightgray", colour = "grey") +
  geom_tile(data = data_box, aes(x = xc, y = yc, width = w, height = w), fill = NA, color = 1, linewidth = 0.5) +
  ggrepel::geom_text_repel(data = data_box, aes(x = xc, y = yc, label = village)) + 
  labs(x = "", y = "") +
  theme(legend.position = "top", axis.title = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), 
        panel.background = element_blank())+
  coord_sf(crs = 'WGS84')

# Gariuai map (fig 1b)
g2 = ggplot(data = elevG) +
  geom_raster(aes(x = x, y = y, fill=srtm_62_14)) +
  geom_point(data = subset(data_plot, village == "Gariuai"), 
             aes(x = long, y = lat, color = ID_AF), size = 2) + 
  geom_point(data = subset(data_plot, village == "Gariuai"), 
             aes(x = long, y = lat), shape = 1, size = 2) + 
  # coord_equal() +
  viridis::scale_fill_viridis(option = "D",
                              limits = range(c(elevS$srtm_62_14, elevG$srtm_62_14))
  ) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  labs(x = "", y = "", title = "Gariuai", color = "", fill="Elevation (m)") +
  guides(color = FALSE, fill=guide_colorbar(title.position = "top")) + 
  theme(legend.position = "top", axis.title = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), 
        plot.title = element_text(hjust = 0.5), 
        panel.background = element_blank()) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))+
  ggspatial::annotation_scale() +
  coord_sf(crs = 'WGS84')

l1 = ggpubr::get_legend(g2)

g2 = g2 + theme(legend.position = "none")
# 
# g2 + ggspatial::annotation_scale() +
#   coord_sf(crs = 'WGS84')

# Samalari map (fig 1c)
g3 = ggplot(data = elevS) +
  geom_raster(aes(x = x, y = y, fill=srtm_62_14)) +

  geom_point(data = subset(data_plot, village == "Samalari"), 
             aes(x = long, y = lat, color = ID_AF), size = 2) + 
  geom_point(data = subset(data_plot, village == "Samalari"), 
             aes(x = long, y = lat), shape = 1, size = 2) + 
  coord_equal() +
  labs(x = "", y = "", title = "Samalari", color = "AF\nsystem", fill="Elevation (m)") +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  viridis::scale_fill_viridis(option = "D",
                              limits = range(c(elevS$srtm_62_14, elevG$srtm_62_14)))+
  guides(color=guide_legend(nrow=2,byrow=TRUE), fill=FALSE) +
  theme(legend.position = "bottom", axis.title = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), 
        plot.title = element_text(hjust = 0.5), 
        panel.background = element_blank()) + 
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))+
  ggspatial::annotation_scale() +
  coord_sf(crs = 'WGS84')

l2 = ggpubr::get_legend(g3)
g3 = g3 + theme(legend.position = "none")

ggpubr::ggarrange(g1, 
                  ggpubr::ggarrange(g2, 
                                    ggpubr::ggarrange(g3, l1, l2, ncol=1, heights = c(4,1,1)), 
                                    widths = c(4,3), labels = c("b", "c")), 
                  heights = c(1, 3), nrow = 2, labels = c("a", ""))

ggsave("figures/mapPlotsSRTM.png", height =6, width = 7)
```

```{r anova}
## identify otuliers
# library(magrittr)
library(rstatix)
dataC %>% 
  group_by(ID_AF) %>%
  identify_outliers(meanAGC)

@@

opar <- par(mai=c(1,1,1.5,1))
plot(tuk.cld)
```

@@

dataC_all <- dataC_all[, .(value = mean(value)), .(village, ID_AF, variable)]

@@

dataC_all[, variable := factor(variable, levels = c("meanAGC", "meanBGC", "meanSC"))]
levels(dataC_all$variable) <- c("AGC", "BGC", "SOC")

@@

```{r fig-3-reg, fig.height = 5, fig.width = 7}
## mixed effect linear regression
lmeReg <- lmerTest::lmer(meanSC ~ meanAGC + (1|village), data = dataC)
# Nakagawa’s R2 for mixed models
R2 = performance::r2_nakagawa(lmeReg)

## figure
ggplot(dataC, aes(color = ID_AF)) +
  geom_point(aes(x = meanAGC, y = meanSC, shape = village), size = 2) + 
  annotate(geom= "text", x = Inf, y = Inf, hjust = 1, vjust = 1, parse = TRUE,
           label = paste0("R^{2}*' (marg.) = '*", round(R2$R2_marginal, 3))) +
  annotate(geom= "text", x = Inf, y = Inf, hjust = 1, vjust = 2, parse = TRUE,
           label = paste0("R^{2}*' (cond.) = '*", round(R2$R2_conditional, 3))) +
  geom_linerange(aes(x = meanAGC, y = meanSC, ymin = lwrSC, ymax = uprSC)) +
  geom_errorbarh(aes(y = meanSC, xmin = lwrAGC, xmax = uprAGC)) +
  geom_abline(intercept = summary(lmeReg)$coefficients[1,1], slope = summary(lmeReg)$coefficients[2,1], lty = 2) +
  labs(color = "AF system", x = "Aboveground C (Mg C/ha)", y = "Soil C (Mg C/ha)") + 
  expand_limits(x = 0, y = 0) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  # scale_linetype_manual(values=c("twodash", "dotted"))+
  theme_classic() 
ggsave("figures/fig-scatterplot-carbon.png", height = 5, width = 7)
```

@@

>>>>

data_soil_C <-
  data_soil[, .(
    meanSC = sum(Cstock),
    SC10 = Cstock[SAMPLE_DEPTH == "0-10"],
    clay = mean(as.numeric(CLAY), na.rm = TRUE)
  ), .(N_PLOT)]

setkey(data_soil_C, "N_PLOT")
```

@@

data_soil_unc = data_soil_unc[, .(
  Cstock = sum(
    (h1 - h0) * 1e8 *  
      BD * Corg/100 * (1-CF) * 1e-6  
  ), 
  Cstock10 = (
    (h1 - h0) * 1e8 *  
      BD * Corg/100 * (1-CF) * 1e-6  
  )[SAMPLE_DEPTH == "0-10"]),
  .(N_PLOT, iter)
]

data_soil_unc = data_soil_unc[, .(
  lwrSC = quantile(Cstock, 0.025), 
  uprSC = quantile(Cstock, 0.975),
  lwrSC10 = quantile(Cstock10, 0.025), 
  uprSC10 = quantile(Cstock10, 0.975)), 
  .(N_PLOT)]
```

```{r combine-agb-soc-data}
# combine AGB and soil C
dataC <- merge(data_agb, data_soil_C, by = "N_PLOT", all=TRUE)

# add soil carbon uncertainty
dataC <- merge(dataC, data_soil_unc, all=TRUE)

dataC[N_PLOT==6, `:=`(ID_VILLAGE = "GD", ID_AF = "CF")]

@@

```{r tab-mean, results = "show"}
# average values per village and SAF type
dataC_mean <- dataC[, .(AGC = paste0(round(mean(meanAGC[!is.na(meanAGC)]), 2), " +/- ", round(sd(meanAGC[!is.na(meanAGC)])/sqrt(length(meanAGC[!is.na(meanAGC)])), 2)), 
                        SC = paste0(round(mean(meanSC[!is.na(meanSC)]), 2), " +/- ", round(sd(meanSC[!is.na(meanSC)])/sqrt(length(meanSC[!is.na(meanSC)])), 2))),
                    .(ID_AF)]
dataC_mean$ID_AF <- factor(dataC_mean$ID_AF, levels = c("CF", "SP", "YA", "HG", "FG"))
dataC_mean = dataC_mean[order(dataC_mean$ID_AF),]
knitr::kable(dataC_mean, col.names = c("Agroforestry system", "Aboveground carbon (Mg/ha)", "Soil organic carbon (Mg/ha)"))
write.csv(dataC_mean, file = "tables/C_mean_SAF.csv", row.names = FALSE)
```

```{r tab-anova, results = "show"}
# 2-way anova 
dataC[, ID_SUCO := substr(ID_VILLAGE, 1, 1)]
anov1 = anova(lm(meanAGC~ID_SUCO+ID_AF, data = dataC))
anov2 = anova(lm(meanSC~ID_SUCO+ID_AF, data = dataC))
tab_anov = data.frame(response = rep(c("AGC", "SOC"), each = 2), 
                      ind_var = rep(c("SUCO", "AF"), 2), 
                      p = round(c(anov1$`Pr(>F)`[1:2], anov2$`Pr(>F)`[1:2]), 3)
)
```

```{r fig-1-map, fig.height =6, fig.width = 7}

@@

data_plot[, village := substr(ID_VILLAGE, 1, 1)]
data_plot[village == "S", village := "Osso Luga"]
data_plot[village == "G", village := "Gariuai"]

data_box = data_plot[, .(xc = mean(long), yc = mean(lat)), .(village)]
data_box[village == "Gariuai", `:=`(w = 0.1, xc = xc + 0.001)]
data_box[village == "Osso Luga", w := 0.05]
data_box[, `:=`(x1 = xc - w/2, x2 = xc + w/2, y1 = yc - w/2, y2 = yc + w/2)]

@@

# geodata::elevation_3s(lon= c(data_box[village == "Osso Luga"]$x1), 
#                       lat= c(data_box[village == "Osso Luga"]$y1), 
#                       path = "data")
timor_map <- map_data("world", region = "Timor-Leste")

g1 = ggplot(timor_map) + 
  annotate(geom = "text", label = "a", x = -Inf, y = Inf, 
           hjust = 0, vjust = 1, fontface = "bold", size = 6) + 
  geom_polygon(aes(x = long, y = lat, group = group), fill="lightgray", colour = "grey") +
  geom_tile(data = data_box, aes(x = xc, y = yc, width = w, height = w), fill = NA, color = 1, linewidth = 0.5) +
  ggrepel::geom_text_repel(data = data_box, aes(x = xc, y = yc, label = village)) + 
  labs(x = "", y = "") +
  theme(legend.position = "top", axis.title = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), 
        panel.background = element_blank())+
  coord_sf(crs = 'WGS84')

# get elevation information
elev = as.data.frame(terra::rast("data/srtm_62_14.tif"), xy = TRUE)
elevS <- subset(elev, x > data_box[village == "Osso Luga"]$x1 & 
                  x < data_box[village == "Osso Luga"]$x2 & 
                  y > data_box[village == "Osso Luga"]$y1 & 
                  y < data_box[village == "Osso Luga"]$y2)
elevS$village = "Osso Luga"
elevG <- subset(elev, x > data_box[village == "Gariuai"]$x1 & 
                  x < data_box[village == "Gariuai"]$x2 & 
                  y > data_box[village == "Gariuai"]$y1 & 
                  y < data_box[village == "Gariuai"]$y2)
elevG$village = "Gariuai"

elevAll = rbind(elevS, elevG)

## Map of villages and plots with elevation
g2 = 
  ggplot(data = elevAll) +
  geom_raster(aes(x = x, y = y, fill=srtm_62_14)) +
  geom_point(data = data_plot, 
             aes(x = long, y = lat, color = ID_AF), size = 2) + 
  geom_point(data = data_plot, 
             aes(x = long, y = lat), shape = 1, size = 2) + 
  # coord_equal() +
  viridis::scale_fill_viridis(option = "D",
                              limits = range(c(elevS$srtm_62_14, elevG$srtm_62_14))
  ) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  labs(x = NULL, y = NULL, color = NULL, fill="Elevation (m)") +
  annotate(geom = "text", label = "b", x = -Inf, y = Inf, 
           hjust = -0.5, vjust = 1, fontface = "bold", size = 6) + 
  annotate(geom = "text", label = "c", x = Inf, y = -Inf, 
           hjust = 12, vjust = -9.8, fontface = "bold", size = 6) + 
  guides(color = FALSE, fill=guide_colorbar(title.position = "top")) +
  theme(legend.position = c(0.8, 0.85), legend.direction="horizontal", 
        axis.title = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), 
        plot.title = element_text(hjust = 0.5), 
        panel.background = element_blank()) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))+
  ggspatial::annotation_scale() +
  coord_sf(crs = 'WGS84')

# get AFS legend
g3 = ggplot(data_plot) +
  geom_point(aes(x = long, y = lat, color = ID_AF)) + 
  labs(color = "AFS") +
  guides(color=guide_legend(ncol=2)) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  theme_classic()
l1 = ggpubr::get_legend(g3)

ggpubr::ggarrange(ggpubr::ggarrange(g1, l1), g2, ncol = 1, heights = c(1,2))

ggsave("figures/mapPlotsSRTM.png", height =4.5, width = 6)

# extract elevation and rainfall for the 2 villages
data_plot$prec <- terra::extract(
  terra::rast("D:/maps/CHELSA/CHELSA_bio12_1981-2010_V.2.1.tif"), 
  cbind(data_plot$long, data_plot$lat)
)
data_plot$elev <- terra::extract(
  terra::rast("data/srtm_62_14.tif"), 
  cbind(data_plot$long, data_plot$lat)
)
data_plot[, ID_SUCO := substr(ID_VILLAGE, 1, 1)]
data_plot[, .(prec = mean(prec), range_prec = paste(range(prec), collapse = " - ")), .(ID_SUCO)]
data_plot[, .(elev = mean(elev), range_elev = paste(range(elev), collapse = " - ")), .(ID_SUCO)]
```

```{r anova}
## identify outliers
# library(magrittr)
library(rstatix)
dataC %>% 
  group_by(ID_AF) %>%
  identify_outliers(meanAGC)

@@

opar <- par(mai=c(1,1,1.5,1))
plot(tuk.cld)

## non parametric test
#updated translation of help page implementation of Nemenyi-Damico-Wolfe-Dunn test
library(coin)
is.factor(dataC$ID_AF)
NDWD <-
  independence_test(meanAGC ~ ID_AF, data = dataC)
# , distribution = approximate(B = 10000),
# ytrafo = function(data) trafo(data, numeric_trafo = rank_trafo),
# xtrafo = mcp_trafo(iv = "Tukey"))

### global p-value
print(pvalue(NDWD))

### sites (I = II) != (III = IV) at alpha = 0.01 (page 244)
print(pvalue(NDWD, method = "single-step"))

#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-

library(tidyverse)
library(ggpubr)
library(rstatix)

# Data preparation
# 
# Here, we’ll use the built-in R data set named PlantGrowth. It contains the weight of plants obtained under a control and two different treatment conditions.

# Re-order the group levels:

# dataC <- dataC %>%
#   reorder_levels(group, order = c("ctrl", "trt1", "trt2"))

dataC %>% 
  group_by(ID_AF) %>%
  get_summary_stats(meanAGC, type = "common")

# Create a box plot of weight by group:

# Question: We want to know if there is any significant difference between the
# average weights of plants in the 3 experimental conditions.

# We’ll use the pipe-friendly kruskal_test() function [rstatix package], a
# wrapper around the R base function kruskal.test().

res.kruskal <- dataC %>% kruskal_test(meanAGC ~ ID_AF)
res.kruskal

# Effect size
#
# The eta squared, based on the H-statistic, can be used as the measure of the
# Kruskal-Wallis test effect size. It is calculated as follow : eta2[H] = (H - k
# + 1)/(n - k); where H is the value obtained in the Kruskal-Wallis test; k is
# the number of groups; n is the total number of observations (M. T. Tomczak and
# Tomczak 2014).
#
# The eta-squared estimate assumes values from 0 to 1 and multiplied by 100
# indicates the percentage of variance in the dependent variable explained by
# the independent variable.
#
# The interpretation values commonly in published literature are: 0.01- < 0.06
# (small effect), 0.06 - < 0.14 (moderate effect) and >= 0.14 (large effect).

dataC %>% kruskal_effsize(meanAGC ~ ID_AF)

# Multiple pairwise-comparisons
# 
# From the output of the Kruskal-Wallis test, we know that there is a significant difference between groups, but we don’t know which pairs of groups are different.
# 
# A significant Kruskal-Wallis test is generally followed up by Dunn’s test to identify which groups are different. It’s also possible to use the Wilcoxon’s test to calculate pairwise comparisons between group levels with corrections for multiple testing.

# Pairwise comparisons
pwc <- dataC %>% 
  dunn_test(meanAGC ~ ID_AF, p.adjust.method = "bonferroni") 
pwc[pwc$p.adj.signif=="*",]
```

@@

dataC_all <- dataC_all[, .(value = mean(value, na.rm = TRUE)), .(village, ID_AF, variable)]

@@

dataC_all[, variable := factor(variable, levels = c("meanAGC", "meanBGC", "meanSC"))]
levels(dataC_all$variable) <- c("AGC", "BGC", "SOC")
dataC_all[, village := factor(village)]
levels(dataC_all$village) <- c("Gariuai", "Osso Luga")

@@

```{r fig-3-reg, fig.height = 4, fig.width = 8}
## mixed effect linear regression
lmeReg <- lmerTest::lmer(meanSC ~ meanAGC + (1|village), data = dataC)
# Nakagawa’s R2 for mixed models
R2 = performance::r2_nakagawa(lmeReg)
summary(lmeReg)

# same for topsoil layer (0-10 cm)
lmeReg10 <- lmerTest::lmer(SC10 ~ meanAGC + (1|village), data = dataC)
# Nakagawa’s R2 for mixed models
R210 = performance::r2_nakagawa(lmeReg10)
summary(lmeReg10)

dfreg = 
  data.frame(
    depth = c("Soil depth: 0-30 cm", "Soil depth: 0-10 cm"), 
    intercept = c(summary(lmeReg)$coefficients[1,1], summary(lmeReg10)$coefficients[1,1]), 
    slope = c(summary(lmeReg)$coefficients[2,1], summary(lmeReg10)$coefficients[2,1]), 
    R2_cond = c(R2$R2_conditional, R210$R2_conditional), 
    R2_marg = c(R2$R2_marginal, R210$R2_marginal)
  )

# change village names
dataC[, village := factor(village)]
levels(dataC$village) <- c("Gariuai", "Osso Luga")

# stack data for figure

dataC_30 = dataC[, c("N_PLOT", "village", "ID_AF",  "meanAGC", "lwrAGC", "uprAGC", "meanSC", "lwrSC", "uprSC")]
dataC_30$depth = "Soil depth: 0-30 cm"
dataC_10 = dataC[, c("N_PLOT", "village", "ID_AF",  "meanAGC", "lwrAGC", "uprAGC", "SC10", "lwrSC10", "uprSC10")]
dataC_10$depth = "Soil depth: 0-10 cm"
colnames(dataC_10) = colnames(dataC_30)
dataC_fig = rbind(dataC_10, dataC_30)

## figure
ggplot(dataC_fig, aes(color = ID_AF)) +
  geom_point(aes(x = meanAGC, y = meanSC, shape = village), size = 2) + 
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (marg.) = '*", round(R2_marg, 3))),
            x = Inf, y = Inf, hjust = 1, vjust = 1.2, parse = TRUE, color = 1) +
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (cond.) = '*", round(R2_cond, 3))),
            x = Inf, y = Inf, hjust = 1, vjust = 2.2, parse = TRUE, color = 1) +
  geom_linerange(aes(x = meanAGC, y = meanSC, ymin = lwrSC, ymax = uprSC)) +
  geom_errorbarh(aes(y = meanSC, xmin = lwrAGC, xmax = uprAGC)) +
  geom_abline(data = dfreg, aes(intercept = intercept, slope = slope), lty = 2) +
  labs(color = "AF system", x = "Aboveground C (Mg C/ha)", y = "Soil C (Mg C/ha)") + 
  expand_limits(x = 0, y = 0) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  facet_wrap(~depth) + 
  theme_classic()

ggsave("figures/fig-scatterplot-carbon.png", height = 4, width = 8)
```

```{r fig-3-reg-10, fig.height = 5, fig.width = 7}
## mixed effect linear regression
lmeReg10 <- lmerTest::lmer(SC10 ~ meanAGC + (1|village), data = dataC)
# Nakagawa’s R2 for mixed models
R2 = performance::r2_nakagawa(lmeReg)

## figure
ggplot(dataC, aes(color = ID_AF)) +
  geom_point(aes(x = meanAGC, y = SC10, shape = village), size = 2) + 
  annotate(geom= "text", x = Inf, y = Inf, hjust = 1, vjust = 1, parse = TRUE,
           label = paste0("R^{2}*' (marg.) = '*", round(R2$R2_marginal, 3))) +
  annotate(geom= "text", x = Inf, y = Inf, hjust = 1, vjust = 2, parse = TRUE,
           label = paste0("R^{2}*' (cond.) = '*", round(R2$R2_conditional, 3))) +
  # geom_linerange(aes(x = meanAGC, y = SC10, ymin = lwrSC, ymax = uprSC)) +
  geom_errorbarh(aes(y = SC10, xmin = lwrAGC, xmax = uprAGC)) +
  geom_abline(intercept = summary(lmeReg)$coefficients[1,1], slope = summary(lmeReg)$coefficients[2,1], lty = 2) +
  labs(color = "AF system", x = "Aboveground C (Mg C/ha)", y = "Soil C (Mg C/ha)") + 
  expand_limits(x = 0, y = 0) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  # scale_linetype_manual(values=c("twodash", "dotted"))+
  theme_classic() 
ggsave("figures/fig-scatterplot-carbon.png", height = 5, width = 7)
```

@@

```{r test-ac-soc-by-depth}
data_soil_agc <- merge(data_soil[, c("N_PLOT", "SAMPLE_DEPTH", "Cstock")], 
                       dataC[, c("N_PLOT","ID_AF", "ID_VILLAGE",  "meanAGC")], by = "N_PLOT")

ggplot(data_soil_agc, aes(x = meanAGC, y = Cstock, col = SAMPLE_DEPTH)) +
  geom_point() +
  geom_smooth(method = "lm")

lm(data = data_soil_agc, Cstock ~ meanAGC * SAMPLE_DEPTH) |> summary()
lm(data = data_soil_agc[SAMPLE_DEPTH == "0-10"], Cstock ~ meanAGC) |> summary()
lm(data = data_soil_agc[SAMPLE_DEPTH == "10-20"], Cstock ~ meanAGC ) |> summary()
lm(data = data_soil_agc[SAMPLE_DEPTH == "20-30"], Cstock ~ meanAGC ) |> summary()
```

```{r compare-lit-values}
litval <- read_excel("data/literature-values.xlsx")
colnames(litval) <- c("system", "pool", "value", "location", "ref")

litval$main_crop <- NA
litval$main_crop[grepl("palm", litval$system)] <- "oil palm"
litval$main_crop[grepl("offee", litval$system)] <- "coffee"
unique(litval$system[is.na(litval$main_crop)])

litval$main_per <- NA
litval$main_per[grepl("nset", litval$system)] <- "enset"
litval$main_per[grepl("Inga", litval$system)] <- "inga"
litval$main_per[grepl("Eucalyptus", litval$system)] <- "eucalyptus"
litval$main_per[grepl("Pinus", litval$system)] <- "pinus"
unique(litval$system[is.na(litval$main_per)])

litval$ID_AF <- NA
litval$ID_AF[grepl("orests|orest |orest$", litval$system)] <- "forest"
litval$ID_AF[grepl("onoculture", litval$system)] <- "monoculture"
litval$ID_AF[!is.na(litval$main_crop) & !is.na(litval$main_per)] <- "two-crops"
litval$ID_AF[grepl("ome garden", litval$system)] <- "HG"
unique(litval$system[is.na(litval$ID_AF)])

litval$var <- as.numeric(gsub(" ", "", tstrsplit(litval$value, "±")[[2]]))
litval$value <- gsub(" ", "", tstrsplit(litval$value, "±")[[1]])

mult_values <- which(sapply(strsplit(litval$value, ",|and"), length)>1)

new_rows = lapply(mult_values, function(i){
  vals = as.numeric(strsplit(litval$value[i], ",|and")[[1]])
  vals = vals[!is.na(vals)]

  x = matrix(litval[i,], ncol = ncol(litval), nrow = length(vals), byrow = TRUE)
  x[, colnames(litval) == "value"] = vals

  x = as.data.frame(x)
  colnames(x) = colnames(litval)
  return(x)
}
)

new_rows = do.call(rbind, new_rows)

litval2 = rbind(new_rows, litval[-mult_values,])
litval = data.frame(system = unlist(litval2$system), 
                    pool = unlist(litval2$pool), 
                    value = unlist(litval2$value), 
                    location = unlist(litval2$location), 
                    ref = unlist(litval2$ref), 
                    main_crop = unlist(litval2$main_crop),
                    main_per = unlist(litval2$main_per), 
                    ID_AF = unlist(litval2$ID_AF), 
                    var = unlist(litval2$var))

```
